Results_setup

### 2020-06-22 src/Result_Setup.Rmd
fixed a bug from Common functions

summary.glm(MLH1.M2.glm.strain.fixed.full)$coefficients

@@

#mouse.total.skel
Q1.lmer_totSC_M1 <- lmer(mean.skel ~ subsp * sex + (1|strain), data= ( mouse.total.skel %>% filter(species == "M.musculus") %>% filter(strain !=  "CAST" ) %>% filter(strain !=  "MOLF" ) %>% filter(strain !=  "HMI" ) %>% filter(strain !=  "AST" ) %>% filter(strain !=  "PERC" ) %>% filter(strain !=  "CZECH" ) )  )

Q1.lmer_totSC_M1_R.sex <- lmer(mean.skel ~ subsp + (1|strain), data=( mouse.total.skel %>% filter(species == "M.musculus") %>% filter(strain !=  "CAST" ) %>% filter(strain !=  "MOLF" ) %>% filter(strain !=  "HMI" ) %>% filter(strain !=  "AST" ) %>% filter(strain !=  "PERC" ) %>% filter(strain !=  "CZECH" ) ))

Q1.lmer_totSC_M1_R.subsp <- lmer(mean.skel ~ sex + (1|strain), data=( mouse.total.skel %>% filter(species == "M.musculus") %>% filter(strain !=  "CAST" ) %>% filter(strain !=  "MOLF" ) %>% filter(strain !=  "HMI" ) %>% filter(strain !=  "AST" ) %>% filter(strain !=  "PERC" ) %>% filter(strain !=  "CZECH" ) ))

@@

Q1.glm_totSC_M2 <- glm(mean.skel ~ subsp*strain * sex, data=  (mouse.total.skel %>% filter(species == "M.musculus") %>% filter(strain !=  "CAST" ) %>% filter(strain !=  "MOLF" ) %>% filter(strain !=  "HMI" ) %>% filter(strain !=  "AST" ) %>% filter(strain !=  "PERC" ) %>% filter(strain !=  "CZECH" ) )  )

@@

Q1.glm_totSC_M3 <- glm(mean.skel ~ strain * sex, data=  (mouse.total.skel %>% filter(species == "M.musculus") %>% filter(strain !=  "CAST" ) %>% filter(strain !=  "MOLF" ) %>% filter(strain !=  "HMI" ) %>% filter(strain !=  "AST" ) %>% filter(strain !=  "PERC" ) %>% filter(strain !=  "CZECH" ) ) )

@@

@@

```{r Q1.M1_short_biv_lmer, echo=FALSE, warning=FALSE, message=FALSE, eval=FALSE}

lmer.Q1_SCLength_short_M1 <- lmer(mean_SC ~ subsp * sex + (1|strain), data=Short.biv_mouse_table, REML = TRUE) 
lmer.Q1_SCLength_short_M1_R.sex <- lmer(mean_SC ~ subsp + (1|strain), data=Short.biv_mouse_table, REML = TRUE) 
lmer.Q1_SCLength_short_M1_R.subsp <- lmer(mean_SC ~ sex + (1|strain), data=Short.biv_mouse_table, REML = TRUE)

Q1lmer.MM_SC_short_interaction  <-drop1(lmer.Q1_SCLength_short_M1, test="Chisq" )$`Pr(Chi)`[2]
Q1lmer.MM_SC_short_sex  <-anova(lmer.Q1_SCLength_short_M1, lmer.Q1_SCLength_short_M1_R.sex)$`Pr(>Chisq)`[2]
Q1lmer.MM_SC_short_subp  <- anova(lmer.Q1_SCLength_short_M1, lmer.Q1_SCLength_short_M1_R.subsp)$`Pr(>Chisq)`[2]
Q1lmer.MM_SC_short_strain  <- exactRLRT(lmer.Q1_SCLength_short_M1)$p.value

#as.data.frame(round(summary(lmer.SCLength_all_MM.M1)$coefficients, 6))#these Dont return p values for the fixed effects

Q1lmer.MM_SC_short_results <- data.frame(sub.sp = Q1lmer.MM_SC_short_subp, 
sex.results =  Q1lmer.MM_SC_short_sex, 
               interaction.pval = Q1lmer.MM_SC_short_interaction,  rand.pval = 
Q1lmer.MM_SC_short_strain)

#Q1lmer.MM_SC_short_results
write.table(Q1lmer.MM_SC_short_results, "~./MLH1repo/ShortSC_Q1_M1.csv", sep=",",row.names = TRUE)

#write_xlsx(Q1lmer.MM_SC_short_results, "~./MLH1repo/ShortSC_Q1_M1.xlsx", col_names = TRUE)

write.xlsx(Q1lmer.MM_SC_short_results, "ShortSC_Q1_M1.xlsx", col.names = TRUE)

@@

Q1.lmer_short_M1 <- lmer(mean_SC ~ subsp * sex + (1|strain), data= ( Short.biv_mouse_table %>% filter(species == "M.musculus") %>% filter(strain !=  "CAST" ) %>% filter(strain !=  "MOLF" ) %>% filter(strain !=  "HMI" ) %>% filter(strain !=  "AST" ) %>% filter(strain !=  "PERC" ) %>% filter(strain !=  "CZECH" ) ) )

Q1.lmer_short_M1_R.sex <- lmer(mean_SC ~ subsp + (1|strain), data= ( Short.biv_mouse_table %>%  filter(species == "M.musculus") %>% filter(strain !=  "CAST" ) %>% filter(strain !=  "MOLF" ) %>% filter(strain !=  "HMI" ) %>% filter(strain !=  "AST" ) %>% filter(strain !=  "PERC" ) %>% filter(strain !=  "CZECH" ) ) )

Q1.lmer_short_M1_R.subsp <- lmer(mean_SC ~ sex + (1|strain), data= ( Short.biv_mouse_table %>% filter(species == "M.musculus") %>% filter(strain !=  "CAST" ) %>% filter(strain !=  "MOLF" ) %>% filter(strain !=  "HMI" ) %>% filter(strain !=  "AST" ) %>% filter(strain !=  "PERC" ) %>% filter(strain !=  "CZECH" ) )  )

@@

write_xlsx(Q1.lmer_short_M1_results, "~./MLH1repo/ShortSC_Q1_M1.xlsx", col_names = TRUE)
```

@@

Q1.glm_short.SC_M2 <- glm(mean_SC ~ subsp * strain * sex, data= ( Short.biv_mouse_table %>% filter(species == "M.musculus") %>% filter(strain !=  "CAST" ) %>% filter(strain !=  "MOLF" ) %>% filter(strain !=  "HMI" ) %>% filter(strain !=  "AST" ) %>% filter(strain !=  "PERC" ) %>% filter(strain !=  "CZECH" ) ) )

@@

```{r Q1.glm_short.SC_M3, echo=FALSE, message=FALSE}
Q1.glm_short.SC_M3 <- glm(mean_SC ~ strain * sex, data= ( Short.biv_mouse_table %>% filter(species == "M.musculus") %>% filter(strain !=  "CAST" ) %>% filter(strain !=  "MOLF" ) %>% filter(strain !=  "HMI" ) %>% filter(strain !=  "AST" ) %>% filter(strain !=  "PERC" ) %>% filter(strain !=  "CZECH" ) )  )

@@

```{r Q1.CO1pos_lmer.M1, echo=FALSE, message=FALSE}

lmer.Q1.nrm1CO_M1 <- lmer(norm.first.foci.pos ~ subsp * sex + (1|strain), 
                          data= ( mouse.level.BivData_table %>% filter(species == "M.musculus") %>% filter(strain !=  "CAST" ) %>% filter(strain !=  "MOLF" ) %>% filter(strain !=  "HMI" ) %>% filter(strain !=  "AST" ) %>% filter(strain !=  "PERC" ) %>% filter(strain !=  "CZECH" ) ) )

lmer.Q1.nrm1CO_M1reduce.sex <- lmer( norm.first.foci.pos ~ subsp  +(1|strain), data=( mouse.level.BivData_table %>% filter(species == "M.musculus") %>% filter(strain !=  "CAST" ) %>% filter(strain !=  "MOLF" ) %>% filter(strain !=  "HMI" ) %>% filter(strain !=  "AST" ) %>% filter(strain !=  "PERC" ) %>% filter(strain !=  "CZECH" ) ) )

lmer.Q1.nrm1CO_M1reduce.subp <- lmer( norm.first.foci.pos ~ sex  +(1|strain), data=( mouse.level.BivData_table %>% filter(species == "M.musculus") %>% filter(strain !=  "CAST" ) %>% filter(strain !=  "MOLF" ) %>% filter(strain !=  "HMI" ) %>% filter(strain !=  "AST" ) %>% filter(strain !=  "PERC" ) %>% filter(strain !=  "CZECH" ) ) )

@@

Q1.glm_F1pos_M2 <- glm(norm.first.foci.pos ~ subsp * strain * sex, data=( mouse.level.BivData_table %>% filter(species == "M.musculus") %>% filter(strain !=  "CAST" ) %>% filter(strain !=  "MOLF" ) %>% filter(strain !=  "HMI" ) %>% filter(strain !=  "AST" ) %>% filter(strain !=  "PERC" ) %>% filter(strain !=  "CZECH" ) ) )

@@

```{r Q1.CO1pos_glm.M3, echo=FALSE, eval=TRUE}

Q1.glm_1CO.pos_M3 <- glm(norm.first.foci.pos ~ strain * sex, data=( mouse.level.BivData_table %>% filter(species == "M.musculus") %>% filter(strain !=  "CAST" ) %>% filter(strain !=  "MOLF" ) %>% filter(strain !=  "HMI" ) %>% filter(strain !=  "AST" ) %>% filter(strain !=  "PERC" ) %>% filter(strain !=  "CZECH" ) ))

#summary(Q1.glm_1CO.pos_M3)

@@

#M1_IFD_2CO_ABS
lmer.IFD.ABS_MM.M1 <- lmer(mean_IFD.2CO_ABS ~ subsp * sex + (1|strain), data= ( mouse.level.BivData_table %>% filter(strain != "CZECH") )) 
lmer.IFD.ABS_MM.M1.reduce.sex <- lmer( mean_IFD.2CO_ABS ~ subsp  +(1|strain), data=( mouse.level.BivData_table %>% filter(strain != "CZECH") ) )
lmer.IFD.ABS_MM.M1.reduce.subp <- lmer( mean_IFD.2CO_ABS ~ sex  +(1|strain), data=( mouse.level.BivData_table %>% filter(strain != "CZECH") ) )

@@

write_xlsx(Q1.IFD.ABS_M1_lmer.results, "~./MLH1repo/ABS.IFD_Q1_M1.xlsx", col_names = TRUE)

#M1_IFD_2CO
lmer.IFD.PER_MM.M1 <- lmer(mean_IFD.2CO_PER ~ subsp * sex + (1|strain), data=( mouse.level.BivData_table %>% filter(strain != "CZECH") ) ) 
lmer.IFD.PER_MM.M1.reduce.sex <- lmer( mean_IFD.2CO_PER ~ subsp  +(1|strain), data=( mouse.level.BivData_table %>% filter(strain != "CZECH") )  )
lmer.IFD.PER_MM.M1.reduce.subp <- lmer( mean_IFD.2CO_PER ~ sex  +(1|strain), data=( mouse.level.BivData_table %>% filter(strain != "CZECH") ) )

@@

write_xlsx(Q1.IFD.PER_M1_lmer.results, "~./MLH1repo/PER.IFD_Q1_M1.xlsx", col_names = TRUE)

```{r Q1.IFD_glm.M2, echo=FALSE, warning=FALSE, message=FALSE}
#mouse.avs_4MM -- is also the bivbased mouse average table 
#Mouse.Table_BivData_4MM #this one is the HetC table (all the Curated BivData)
glm.Q1_IFD.ABS.M2  <- glm(mean_IFD.2CO_ABS ~ subsp * sex * strain, data= ( mouse.level.BivData_table %>% filter(strain != "CZECH") )  )
summry.glm.Q1_IFD.ABS.M2 <- summary(glm.Q1_IFD.ABS.M2)

@@

#PER
glm.Q1_IFD.PER.M2 <- glm(mean_IFD.2CO_PER ~ subsp * sex * strain, data= ( mouse.level.BivData_table %>% filter(strain != "CZECH") ) )
summry.glm.Q1_IFD.PER.M2 <- summary(glm.Q1_IFD.PER.M2)

@@

glm.Q1_IFD.ABS.M3  <- glm(mean_IFD.2CO_ABS ~  sex * strain, data=( mouse.level.BivData_table %>% filter(strain != "CZECH") ))
summry.glm.Q1_IFD.ABS.M3 <- summary(glm.Q1_IFD.ABS.M3)

@@

#PER
glm.Q1_IFD.PER.M3  <- glm(mean_IFD.2CO_PER ~ sex * strain, data=( mouse.level.BivData_table %>% filter(strain != "CZECH") ) )
summry.glm.Q1_IFD.PER.M3 <- summary(glm.Q1_IFD.PER.M3)
#round(summry.glm.Q1_IFD.PER.M3$coefficients[,c(1,4)],5)

@@

@@

Q2.glm_mus.av_totSC_M4.2 <- glm(mean.skel ~ strain, data= mouse.total.skel %>% filter(sex == "male") %>% filter(species == "M.musculus") %>% filter(subsp != "Cast"))
sum.Q2.glm_mus.av_totSC_M4.2  <- summary(Q2.glm_mus.av_totSC_M4.2)
#round(summary(sum.Q2.glm_mus.av_totSC_M2)$coefficients[,c(1,4)], 6)

>>>>

#summary.glm(MLH1.M2.glm.strain.fixed.full)$coefficients

@@

#mouse.total.skel
Q1.lmer_totSC_M1 <- lmer(mean.skel ~ subsp * sex + (1|strain), data= ( mouse.total.skel %>% filter(species == "M.musculus") %>% filter(strain !=  "CAST" ) %>% filter(strain !=  "MOLF" ) %>% filter(strain !=  "HMI" ) %>% filter(strain !=  "AST" ) %>% filter(strain !=  "PERC" ) %>% filter(strain !=  "CZECH" ) %>% filter(strain !=  "TOM" ))  )

Q1.lmer_totSC_M1_R.sex <- lmer(mean.skel ~ subsp + (1|strain), data=( mouse.total.skel %>% filter(species == "M.musculus") %>% filter(strain !=  "CAST" ) %>% filter(strain !=  "MOLF" ) %>% filter(strain !=  "HMI" ) %>% filter(strain !=  "AST" ) %>% filter(strain !=  "PERC" ) %>% filter(strain !=  "CZECH" ) %>% filter(strain !=  "TOM" ) ))

Q1.lmer_totSC_M1_R.subsp <- lmer(mean.skel ~ sex + (1|strain), data=( mouse.total.skel %>% filter(species == "M.musculus") %>% filter(strain !=  "CAST" ) %>% filter(strain !=  "MOLF" ) %>% filter(strain !=  "HMI" ) %>% filter(strain !=  "AST" ) %>% filter(strain !=  "PERC" ) %>% filter(strain !=  "CZECH" ) %>% filter(strain !=  "TOM" ) ) )

@@

Q1.glm_totSC_M2 <- glm(mean.skel ~ subsp*strain * sex, data=  (mouse.total.skel %>% filter(species == "M.musculus") %>% filter(strain !=  "CAST" ) %>% filter(strain !=  "MOLF" ) %>% filter(strain !=  "HMI" ) %>% filter(strain !=  "AST" ) %>% filter(strain !=  "PERC" ) %>% filter(strain !=  "CZECH" ) %>% filter(strain !=  "TOM" ) )  )

@@

Q1.glm_totSC_M3 <- glm(mean.skel ~ strain * sex, data=  (mouse.total.skel %>% filter(species == "M.musculus") %>% filter(strain !=  "CAST" ) %>% filter(strain !=  "MOLF" ) %>% filter(strain !=  "HMI" ) %>% filter(strain !=  "AST" ) %>% filter(strain !=  "PERC" ) %>% filter(strain !=  "CZECH" ) %>% filter(strain !=  "TOM" ) ) )

@@

write.xlsx(as.data.frame(summary.glm(Q1.glm_totSC_M3)$coefficients), "TotalSC_Q1_M3.xlsx", col.names = TRUE, row.names = TRUE)

@@

@@

Q1.lmer_short_M1 <- lmer(mean_SC ~ subsp * sex + (1|strain), data= ( Short.biv_mouse_table %>% filter(species == "M.musculus") %>% filter(strain !=  "CAST" ) %>% filter(strain !=  "MOLF" ) %>% filter(strain !=  "HMI" ) %>% filter(strain !=  "AST" ) %>% filter(strain !=  "PERC" ) %>% filter(strain !=  "CZECH" ) %>% filter(strain !=  "TOM" ) ) )

Q1.lmer_short_M1_R.sex <- lmer(mean_SC ~ subsp + (1|strain), data= ( Short.biv_mouse_table %>%  filter(species == "M.musculus") %>% filter(strain !=  "CAST" ) %>% filter(strain !=  "MOLF" ) %>% filter(strain !=  "HMI" ) %>% filter(strain !=  "AST" ) %>% filter(strain !=  "PERC" ) %>% filter(strain !=  "CZECH" ) %>% filter(strain !=  "TOM" ) ) )

Q1.lmer_short_M1_R.subsp <- lmer(mean_SC ~ sex + (1|strain), data= ( Short.biv_mouse_table %>% filter(species == "M.musculus") %>% filter(strain !=  "CAST" ) %>% filter(strain !=  "MOLF" ) %>% filter(strain !=  "HMI" ) %>% filter(strain !=  "AST" ) %>% filter(strain !=  "PERC" ) %>% filter(strain !=  "CZECH" )  %>% filter(strain !=  "TOM" ) )  )

@@

#write_xlsx(Q1.lmer_short_M1_results, "~./MLH1repo/ShortSC_Q1_M1.xlsx", col_names = TRUE)
write.xlsx(Q1.lmer_short_M1_results, "ShortSC_Q1_M1.xlsx", col.names = TRUE)

@@

Q1.glm_short.SC_M2 <- glm(mean_SC ~ subsp * strain * sex, data= ( Short.biv_mouse_table %>% filter(species == "M.musculus") %>% filter(strain !=  "CAST" ) %>% filter(strain !=  "MOLF" ) %>% filter(strain !=  "HMI" ) %>% filter(strain !=  "AST" ) %>% filter(strain !=  "PERC" ) %>% filter(strain !=  "CZECH" ) %>% filter(strain !=  "TOM" ) ) )

@@

```{r Q1.glm_short.SC_M3, echo=FALSE, message=FALSE}

Q1.glm_short.SC_M3 <- glm(mean_SC ~ strain * sex, data= ( Short.biv_mouse_table %>% filter(species == "M.musculus") %>% filter(strain !=  "CAST" ) %>% filter(strain !=  "MOLF" ) %>% filter(strain !=  "HMI" ) %>% filter(strain !=  "AST" ) %>% filter(strain !=  "PERC" ) %>% filter(strain !=  "CZECH" ) %>% filter(strain !=  "TOM" ) )  )

@@

```{r Q1.CO1pos_lmer.M1, echo=FALSE, message=FALSE}
mouse.level.BivData_table$subsp <- factor(mouse.level.BivData_table$subsp, ordered = FALSE)
mouse.level.BivData_table$sex <- factor(mouse.level.BivData_table$sex, ordered = FALSE)
mouse.level.BivData_table$strain <- factor(mouse.level.BivData_table$strain, ordered = FALSE)
mouse.level.BivData_table$species <- factor(mouse.level.BivData_table$species, ordered = FALSE)

lmer.Q1.nrm1CO_M1 <- lmer(norm.first.foci.pos ~ subsp * sex + (1|strain), 
                          data= ( mouse.level.BivData_table %>% filter(species == "M.musculus") %>% filter(strain !=  "CAST" ) %>% filter(strain !=  "MOLF" ) %>% filter(strain !=  "HMI" ) %>% filter(strain !=  "AST" ) %>% filter(strain !=  "PERC" ) %>% filter(strain !=  "CZECH" ) %>% filter(strain !=  "TOM" ) ) )

lmer.Q1.nrm1CO_M1reduce.sex <- lmer( norm.first.foci.pos ~ subsp  +(1|strain), data=( mouse.level.BivData_table %>% filter(species == "M.musculus") %>% filter(strain !=  "CAST" ) %>% filter(strain !=  "MOLF" ) %>% filter(strain !=  "HMI" ) %>% filter(strain !=  "AST" ) %>% filter(strain !=  "PERC" ) %>% filter(strain !=  "CZECH" )%>% filter(strain !=  "TOM" ) ) )

lmer.Q1.nrm1CO_M1reduce.subp <- lmer( norm.first.foci.pos ~ sex  +(1|strain), data=( mouse.level.BivData_table %>% filter(species == "M.musculus") %>% filter(strain !=  "CAST" ) %>% filter(strain !=  "MOLF" ) %>% filter(strain !=  "HMI" ) %>% filter(strain !=  "AST" ) %>% filter(strain !=  "PERC" ) %>% filter(strain !=  "CZECH" ) %>% filter(strain !=  "TOM" )) )

@@

Q1.glm_F1pos_M2 <- glm(norm.first.foci.pos ~ subsp * strain * sex, data=( mouse.level.BivData_table %>% filter(species == "M.musculus") %>% filter(strain !=  "CAST" ) %>% filter(strain !=  "MOLF" ) %>% filter(strain !=  "HMI" ) %>% filter(strain !=  "AST" ) %>% filter(strain !=  "PERC" ) %>% filter(strain !=  "CZECH" ) %>% filter(strain !=  "TOM" ) ) )

@@

```{r Q1.CO1pos_glm.M3, echo=FALSE, eval=TRUE}
#in case factors aren't ordered
mouse.level.BivData_table$subsp <- factor(mouse.level.BivData_table$subsp, ordered = FALSE)
mouse.level.BivData_table$sex <- factor(mouse.level.BivData_table$sex, ordered = FALSE)
mouse.level.BivData_table$strain <- factor(mouse.level.BivData_table$strain, ordered = FALSE)

Q1.glm_1CO.pos_M3 <- glm(norm.first.foci.pos ~ strain * sex, data=( mouse.level.BivData_table %>% filter(species == "M.musculus") %>% filter(strain !=  "CAST" ) %>% filter(strain !=  "MOLF" ) %>% filter(strain !=  "HMI" ) %>% filter(strain !=  "AST" ) %>% filter(strain !=  "PERC" ) %>% filter(strain !=  "CZECH" ) %>% filter(strain !=  "TOM" ) ))

@@

mouse.level.BivData_table$subsp <- factor(mouse.level.BivData_table$subsp, ordered = FALSE)
mouse.level.BivData_table$sex <- factor(mouse.level.BivData_table$sex, ordered = FALSE)
mouse.level.BivData_table$strain <- factor(mouse.level.BivData_table$strain, ordered = FALSE)
mouse.level.BivData_table$species <- factor(mouse.level.BivData_table$species, ordered = FALSE)

#No MOLF female for curated biv data

#M1_IFD_2CO_ABS
lmer.IFD.ABS_MM.M1 <- lmer(mean_IFD.2CO_ABS ~ subsp * sex + (1|strain), data= ( mouse.level.BivData_table %>% filter(species == "M.musculus") %>% filter(strain !=  "CAST" ) %>% filter(strain !=  "MOLF" ) %>% filter(strain !=  "HMI" ) %>% filter(strain !=  "AST" ) %>% filter(strain !=  "PERC" ) %>% filter(strain !=  "CZECH" ) %>% filter(strain !=  "TOM" ) )
                           )

lmer.IFD.ABS_MM.M1.reduce.sex <- lmer( mean_IFD.2CO_ABS ~ subsp  +(1|strain), data=( mouse.level.BivData_table %>% filter(species == "M.musculus") %>% filter(strain !=  "CAST" ) %>% filter(strain !=  "MOLF" ) %>% filter(strain !=  "HMI" ) %>% filter(strain !=  "AST" ) %>% filter(strain !=  "PERC" ) %>% filter(strain !=  "CZECH" ) %>% filter(strain !=  "TOM" ) ) )

lmer.IFD.ABS_MM.M1.reduce.subp <- lmer( mean_IFD.2CO_ABS ~ sex  +(1|strain), data=( mouse.level.BivData_table %>% filter(species == "M.musculus") %>% filter(strain !=  "CAST" ) %>% filter(strain !=  "MOLF" ) %>% filter(strain !=  "HMI" ) %>% filter(strain !=  "AST" ) %>% filter(strain !=  "PERC" ) %>% filter(strain !=  "CZECH" ) %>% filter(strain !=  "TOM" ) ) )

@@

#write_xlsx(Q1.IFD.ABS_M1_lmer.results, "~./MLH1repo/ABS.IFD_Q1_M1.xlsx", col_names = TRUE)

write.xlsx(Q1.IFD.ABS_M1_lmer.results, "ABS.IFD_Q1_M1.xlsx", col.names = TRUE)

oo <- ( mouse.level.BivData_table %>% filter(species == "M.musculus") %>% filter(strain !=  "CAST" ) %>% filter(strain !=  "MOLF" ) %>% filter(strain !=  "HMI" ) %>% filter(strain !=  "AST" ) %>% filter(strain !=  "PERC" ) %>% filter(strain !=  "CZECH" ) %>% filter(strain !=  "TOM" ) )

#M1_IFD_2CO
lmer.IFD.PER_MM.M1 <- lmer(mean_IFD.2CO_PER ~ subsp * sex + (1|strain), data=
                           ( mouse.level.BivData_table %>% filter(species == "M.musculus") %>% filter(strain !=  "CAST" ) %>% filter(strain !=  "MOLF" ) %>% filter(strain !=  "HMI" ) %>% filter(strain !=  "AST" ) %>% filter(strain !=  "PERC" ) %>% filter(strain !=  "CZECH" ) %>% filter(strain !=  "TOM" ) )
                           )

lmer.IFD.PER_MM.M1.reduce.sex <- lmer( mean_IFD.2CO_PER ~ subsp  +(1|strain), data=( mouse.level.BivData_table %>% filter(species == "M.musculus") %>% filter(strain !=  "CAST" ) %>% filter(strain !=  "MOLF" ) %>% filter(strain !=  "HMI" ) %>% filter(strain !=  "AST" ) %>% filter(strain !=  "PERC" ) %>% filter(strain !=  "CZECH" ) %>% filter(strain !=  "TOM" ) )  )

lmer.IFD.PER_MM.M1.reduce.subp <- lmer( mean_IFD.2CO_PER ~ sex  +(1|strain), data= ( mouse.level.BivData_table %>% filter(species == "M.musculus") %>% filter(strain !=  "CAST" ) %>% filter(strain !=  "MOLF" ) %>% filter(strain !=  "HMI" ) %>% filter(strain !=  "AST" ) %>% filter(strain !=  "PERC" ) %>% filter(strain !=  "CZECH" ) %>% filter(strain !=  "TOM" ) )
                                        )

@@

#write_xlsx(Q1.IFD.PER_M1_lmer.results, "~./MLH1repo/PER.IFD_Q1_M1.xlsx", col_names = TRUE)

write.xlsx(Q1.IFD.PER_M1_lmer.results, "PER.IFD_Q1_M1.xlsx", col.names = TRUE)

```{r Q1.IFD_glm.M2, echo=FALSE, warning=FALSE, message=FALSE}
#mouse.avs_4MM -- is also the bivbased mouse average table 
#Mouse.Table_BivData_4MM #this one is the HetC table (all the Curated BivData)

glm.Q1_IFD.ABS.M2  <- glm(mean_IFD.2CO_ABS ~ subsp * sex * strain, data= ( mouse.level.BivData_table %>% filter(species == "M.musculus") %>% filter(strain !=  "CAST" ) %>% filter(strain !=  "MOLF" ) %>% filter(strain !=  "HMI" ) %>% filter(strain !=  "AST" ) %>% filter(strain !=  "PERC" ) %>% filter(strain !=  "CZECH" ) %>% filter(strain !=  "TOM" ) )
                          )

summry.glm.Q1_IFD.ABS.M2 <- summary(glm.Q1_IFD.ABS.M2)

@@

#PER
glm.Q1_IFD.PER.M2 <- glm(mean_IFD.2CO_PER ~ subsp * sex * strain, data= ( mouse.level.BivData_table %>% filter(species == "M.musculus") %>% filter(strain !=  "CAST" ) %>% filter(strain !=  "MOLF" ) %>% filter(strain !=  "HMI" ) %>% filter(strain !=  "AST" ) %>% filter(strain !=  "PERC" ) %>% filter(strain !=  "CZECH" ) %>% filter(strain !=  "TOM" ) )
                         )

summry.glm.Q1_IFD.PER.M2 <- summary(glm.Q1_IFD.PER.M2)

@@

glm.Q1_IFD.ABS.M3  <- glm(mean_IFD.2CO_ABS ~  sex * strain, data=( mouse.level.BivData_table %>% filter(species == "M.musculus") %>% filter(strain !=  "CAST" ) %>% filter(strain !=  "MOLF" ) %>% filter(strain !=  "HMI" ) %>% filter(strain !=  "AST" ) %>% filter(strain !=  "PERC" ) %>% filter(strain !=  "CZECH" ) %>% filter(strain !=  "TOM" ) )
                          )
summry.glm.Q1_IFD.ABS.M3 <- summary(glm.Q1_IFD.ABS.M3)

@@

#PER
glm.Q1_IFD.PER.M3  <- glm(mean_IFD.2CO_PER ~ sex * strain, data=( mouse.level.BivData_table %>% filter(species == "M.musculus") %>% filter(strain !=  "CAST" ) %>% filter(strain !=  "MOLF" ) %>% filter(strain !=  "HMI" ) %>% filter(strain !=  "AST" ) %>% filter(strain !=  "PERC" ) %>% filter(strain !=  "CZECH" ) %>% filter(strain !=  "TOM" ) )
                          )
summry.glm.Q1_IFD.PER.M3 <- summary(glm.Q1_IFD.PER.M3)
#round(summry.glm.Q1_IFD.PER.M3$coefficients[,c(1,4)],5)

@@

re-write the blocks for M4 M5 MLH1 to total SC. to check results

```{r Female.specific.glm.M4.M5-temp, echo=FALSE, eval=FALSE}
#Change MLH1 to mean_skel

#mean.skel
#mouse.total.skel
mouse.total.skel$strain <- factor(mouse.total.skel$strain, ordered = F)
mouse.total.skel$subsp <- factor(mouse.total.skel$subsp, ordered = F)

```{r tot.SC.Male.specific.glm.M4.M5, echo=FALSE, eval=TRUE}
#mean.skel
#mouse.total.skel

#M4
totSC.male.glm.M4 <- glm(mean.skel ~ subsp * strain, data=(mouse.total.skel %>% filter(sex == "male")  %>% filter(subsp != "Cast") ) %>% filter(species == "M.musculus")   )

sum_totSC.male.glm.M4 <- summary(totSC.male.glm.M4)

#write.table(sum_MLH1.male.glm.M4$coefficients, "~./MLH1repo/MLH1_M4_male_glm.csv", sep=",",row.names = TRUE)

write.xlsx(as.data.frame(sum_totSC.male.glm.M4$coefficients), "TotSC.male.glm.M4.xlsx", col.names = TRUE, row.names = TRUE)

#M5
totSC.male.glm.M5 <- glm(mean.skel ~ strain, data= 
    (mouse.total.skel %>% filter(sex == "male")  %>% filter(subsp != "Cast") %>% filter(species == "M.musculus")) )

sum_totSC.male.glm.M5 <- summary(totSC.male.glm.M5)

#write.table(sum_MLH1.male.glm.M5$coefficients, "~./MLH1repo/MLH1_M5_male_glm.csv", sep=",",row.names = TRUE)

write.xlsx(as.data.frame( sum_totSC.male.glm.M5$coefficients), "TotSC.male.glm.M5.xlsx", col.names = TRUE, row.names = TRUE)

@@

Q2.glm_mus.av_totSC_M4.2 <- glm(mean.skel ~ strain, data= mouse.total.skel %>% filter(sex == "male") %>% filter(species == "M.musculus") %>% filter(subsp != "Cast"))

sum.Q2.glm_mus.av_totSC_M4.2  <- summary(Q2.glm_mus.av_totSC_M4.2)
#round(summary(sum.Q2.glm_mus.av_totSC_M2)$coefficients[,c(1,4)], 6)
